Testing atlantisom: generate census length comps for Norwegian Barents Sea Atlantis

### 2019-05-11 visualization_Rmd/NOBATrueLengthCompTest.Rmd
first try NOBA length comps

---
title: "Testing atlantisom: generate census length comps for California Current Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

This page has visualizations for the CCA model example, Atlantis Summit Common Scenario 1. For full explanation of methods, see the file linked at the beginning of each section.

@@

initCCA <- TRUE
initNEUS <- FALSE
initNOBA <- FALSE

@@

ss_numsallhigh <- numsallhigh[numsallhigh$species == "Yelloweye_rockfish",]
ss_structnall <- structnall[structnall$species == "Yelloweye_rockfish",]
ss_resnall <- resnall[resnall$species == "Yelloweye_rockfish",]

@@

```{r allspplength, eval=FALSE, echo=TRUE}

@@

ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Herring")

>>>>

---
title: "Testing atlantisom: generate census length comps for Norwegian Barents Sea Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

This page has visualizations for the NOBA model example, CERES Global Sustainability. For full explanation of methods, see the file linked at the beginning of each section.

@@

initCCA <- FALSE
initNEUS <- FALSE
initNOBA <- TRUE

@@

ss_numsallhigh <- numsallhigh[numsallhigh$species == "Green_halibut",]
ss_structnall <- structnall[structnall$species == "Green_halibut",]
ss_resnall <- resnall[resnall$species == "Green_halibut",]

@@

```{r allspplength, echo=TRUE}

@@

ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Norwegian_ssh")
